\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-10-26 AffineLieAlgebras/InformalNotes/article.tex
One picture added

\begin{comment}
  The problem of computation of the branching coefficients is very important. Why else would we study it??
  It has major applications in physics of which nobody is aware. Blah-blah-blah.
\end{comment}

@@

The extended Dynkin diagram of $B_2$ 
\begin{equation}
  \label{eq:8}
  \begin{diagram}
    \node{\circ}\arrow{e}{}\node{\circ}\arrow{e}{}\node{\circ}\\ \\
    \node{\circ}\node[2]{\circ}
  \end{diagram}
\end{equation}
We then drop central node and get the embedding $A_1\otimes A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
\begin{comment}
  Consider special embeddings
\end{comment}

@@

\subsection{Affine Lie algebras}
\label{sec:affine-lie-algebras}

\subsection{Embedding of finite-dimensional algebra into affine algebra}
\label{sec:embedd-finite-dimens}

\subsection{Embedding of the affine algebra into affine algebra}
\label{sec:embedd-affine-algebr}

\section{Physical applications}
\label{sec:phys-appl}

Branching coefficients for the embedding of affine Lie subalgebra into
affine Lie algebra can be used to construct modular invariant
partition functions of Wess-Zumino-Novikov-Witten models.

@@

\section{Conclusion}
\label{sec:conclusion}

\bibliography{article}{}
\bibliographystyle{utphys}

>>>>

\begin{comment}
  Write here about the problem and possible applications in physics.
\end{comment}

@@

The extended Dynkin diagram of $B_2$ 
\begin{figure}[ph]
  \centering
  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
We then drop central node and get the embedding $A_1\otimes A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
\begin{comment}
  Consider special embeddings
\end{comment}

@@

\begin{comment}
  Another examples?
\end{comment}
\subsection{Affine Lie algebras}
\label{sec:affine-lie-algebras}
\begin{comment}
  What examples should we include here?
\end{comment}
\subsubsection{Embedding of finite-dimensional algebra into affine algebra}
\label{sec:embedd-finite-dimens}

\subsubsection{Embedding of the affine algebra into affine algebra}
\label{sec:embedd-affine-algebr}

\section{Physical applications}
\label{sec:phys-appl}
\begin{comment}
  Rewrite it in more scientific style or drop this section.
\end{comment}
Branching coefficients for the embedding of affine Lie subalgebra into
affine Lie algebra can be used to construct modular invariant
partition functions of Wess-Zumino-Novikov-Witten models.

@@

\begin{comment}
  We need some real examples
\end{comment}
\section{Conclusion}
\label{sec:conclusion}
\begin{comment}
  Write it
\end{comment}
\begin{comment}
  What about acknowledgements? 
\end{comment}
\bibliography{article}{}
\bibliographystyle{utphys}
